\LARGE Untangling the link between traits, size and growth rate in plants

### 2015-04-29 figure_conceptual.tex
General tidy, remove outdated material, rename variables

\documentclass{beamer}
\usepackage[size=a4, orientation=portrait]{beamerposter}
\setbeamertemplate{navigation symbols}{}
\setbeamersize{text margin left=0em,text margin right=0em}

@@

\node at ($(current page.south)+ (0cm, 23cm)$) (top){};

@@

\defineRow{0}{thisrow}
\rowtitle{Biomass production}
\firstcol{1}{$\frac{\textrm{d}P}{\textrm{d}t}$}{figures/F2_mass_production_net_production}{}
\othercol{2}{$Y$}{figures/empty_box}{$\times$}
\othercol{3}{$\Bigg(A$}{figures/F2_mass_production_assimilation}{-}
\othercol{4}{\ $R$}{figures/F2_mass_production_respiration}{$\Bigg)$}
\othercol{5}{$-T$}{figures/F2_mass_production_turnover}{}
\rowlabel{(1)}

@@

\defineRow{2}{thisrow}
\rowtitle{Leaf-area growth}
\firstcol{1}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}t}$}{figures/F2_leaf_area_growth_dleaf_area_dt}{}
\othercol{2}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}m_{\textrm{t}}}$}{figures/F2_leaf_area_growth_leaf_fraction}{$\times$}
\othercol{3}{$\frac{\textrm{d}m_{\textrm{t}}}{\textrm{d}P}$}{figures/F2_leaf_area_growth_leaf_fraction}{$\times$}
\othercol{4}{$\frac{\textrm{d}P}{\textrm{d}t}$}{figures/F2_leaf_area_growth_net_production}{}
\rowlabel{(3)}

@@

\textbox{$(current page.south)+ (0cm, 3cm)$}{Plant height (m)}

>>>>

\documentclass{beamer}
\usepackage[size=custom, width=21, height=27, scale=1.0, orientation=portrait]{beamerposter}
\setbeamertemplate{navigation symbols}{}
\setbeamersize{text margin left=0em,text margin right=0em}

@@

\node at ($(current page.south)+ (0cm, 20cm)$) (top){};

@@

\defineRow{0}{thisrow}
\rowtitle{Biomass production}
\firstcol{1}{$\frac{\textrm{d}b}{\textrm{d}t}$}{figures/F2_mass_production_net_production}{}
\othercol{2}{$y$}{figures/empty_box}{$\times$}
\othercol{3}{$\Bigg(A$}{figures/F2_mass_production_assimilation}{-}
\othercol{4}{\ $R$}{figures/F2_mass_production_respiration}{$\Bigg)$}
\othercol{5}{$-T$}{figures/F2_mass_production_turnover}{}
\rowlabel{(1)}

@@

\defineRow{2}{thisrow}
\rowtitle{Leaf-area growth}
\firstcol{1}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}t}$}{figures/F2_leaf_area_growth_dleaf_area_dt}{}
\othercol{2}{$\frac{\textrm{d}a_{\textrm{l}}}{\textrm{d}m_{\textrm{t}}}$}{figures/F2_leaf_area_growth_leaf_fraction}{$\times$}
\othercol{3}{$\frac{\textrm{d}m_{\textrm{t}}}{\textrm{d}b}$}{figures/F2_leaf_area_growth_leaf_fraction}{$\times$}
\othercol{4}{$\frac{\textrm{d}b}{\textrm{d}t}$}{figures/F2_leaf_area_growth_net_production}{}
\rowlabel{(3)}

@@

\textbox{$(current page.south)+ (0cm, 0.5cm)$}{Plant height (m)}
